
          %%%%% ~~~~~~~~~~~~~~~~~~~~ %%%%%

\section{Weak convergence in $l^{\infty}(T)$}
\setcounter{theorem}{0}
\setcounter{equation}{0}

%\cite{vanDerVaart1996}
%\cite{Kosorok2008}

%\renewcommand{\theenumi}{\alph{enumi}}
%\renewcommand{\labelenumi}{\textnormal{(\theenumi)}$\;\;$}
\renewcommand{\theenumi}{\roman{enumi}}
\renewcommand{\labelenumi}{\textnormal{(\theenumi)}$\;\;$}

          %%%%% ~~~~~~~~~~~~~~~~~~~~ %%%%%

\begin{lemma}[Lemma 1.5.2, p.35, \cite{vanDerVaart1996}]
\mbox{}\vskip 0.1cm
\noindent
Suppose:
\begin{itemize}
\item
	$T$ is a non-empty set.
	$l^{\infty}(T)$ is the Banach space of uniformly bounded $\Re$-valued functions defined on $T$
	equipped with the supremum norm.
	$\mathcal{B}$ is the Borel $\sigma$-algebra of $l^{\infty}(T)$.
\item
	For each $n\in\N$, $(\Omega_{n},\mathcal{A}_{n},\mu_{n})$ is a probability space, and
	\,$\left\{\,\overset{{\color{white}.}}{X}_{n}(t):(\Omega_{n},\mathcal{A}_{n},\mu_{n})\longrightarrow\Re\,\right\}_{t\in T}$
	is an $\Re$-valued stochastic process indexed by $T$.
\item
	The corresponding sequence
	$\left\{\,
		X_{n} : \Omega_{n}
		\overset{{\color{white}-}}{\longrightarrow}
		l^{\infty}(T)\,\right\}_{n\in\N}$
	of (not necessarily measurable) $l^{\infty}(T)$-valued maps
	is asymptotically tight.
\end{itemize}
Then,
\,$\left\{\,X_{n} : \Omega_{n}\overset{{\color{white}-}}{\longrightarrow}l^{\infty}(T)\,\right\}_{n\in\N}$
is asymptotically measurable if and only if
\,$\left\{\,\overset{{\color{white}.}}{X}_{n}(t) : (\Omega_{n},\mathcal{A}_{n},\mu_{n}) \longrightarrow \Re\,\right\}_{n\in\N}$
is asymptotically measurable, for each $t \in T$.
\end{lemma}
\proof
\qed

          %%%%% ~~~~~~~~~~~~~~~~~~~~ %%%%%

\begin{lemma}[Lemma 1.5.3, p.35, \cite{vanDerVaart1996}]
\label{FiniteDimensionalProjectionsDetermineTightLaws}
\mbox{}\vskip 0.1cm
\noindent
Suppose:
\begin{itemize}
\item
	$T$ is a non-empty set.
	$l^{\infty}(T)$ is the Banach space of uniformly bounded $\Re$-valued functions defined on $T$
	equipped with the supremum norm.
	$\mathcal{B}$ is the Borel $\sigma$-algebra of $l^{\infty}(T)$.
\item
	$X_{1} : (\Omega_{1},\mathcal{A}_{1},\mu_{1}) \longrightarrow l^{\infty}(T)$
	and
	$X_{2} : (\Omega_{2},\mathcal{A}_{2},\mu_{2}) \longrightarrow l^{\infty}(T)$
	are two $l^{\infty}(T)$-valued random variables
	(i.e. $X_{1}$ is $(\mathcal{A}_{1},\mathcal{B})$-measurable and
	$X_{2}$ is $(\mathcal{A}_{2},\mathcal{B})$-measurable).
\item
	The probability measures $L_{X_{1}}$ and $L_{X_{2}}$ induced on $l^{\infty}(T)$
	by $X_{1}$ and $X_{2}$, respectively, are both {\color{red}tight}.
\end{itemize}
Then,
\,$L_{X_{1}} = L_{X_{2}} \in \mathcal{M}_{1}(l^{\infty}(T),\mathcal{B})$\,
if and only if
every pair of corresponding finite-dimensional projections of $X_{1}$ and $X_{2}$
induce the same probability measure.
\end{lemma}
\proof
\qed

          %%%%% ~~~~~~~~~~~~~~~~~~~~ %%%%%

\begin{theorem}[Theorem 1.5.4, p.35, \cite{vanDerVaart1996}]
\mbox{}\vskip 0.1cm
\noindent
Suppose:
\begin{itemize}
\item
	$T$ is a non-empty set.
	$l^{\infty}(T)$ is the Banach space of uniformly bounded $\Re$-valued functions defined on $T$
	equipped with the supremum norm.
	$\mathcal{B}$ is the Borel $\sigma$-algebra of $l^{\infty}(T)$.
\item
	For each $n\in\N$, $(\Omega_{n},\mathcal{A}_{n},\mu_{n})$ is a probability space, and
	\,$\left\{\,\overset{{\color{white}.}}{X}_{n}(t):(\Omega_{n},\mathcal{A}_{n},\mu_{n})\longrightarrow\Re\,\right\}_{t\in T}$
	is an $\Re$-valued stochastic process indexed by $T$ with uniformly bounded sample paths.
\item
	Let $\left\{\,X_{n} : \Omega_{n}
	\overset{{\color{white}-}}{\longrightarrow}l^{\infty}(T)\;\right\}_{n\in\N}$
	be the corresponding sequence of (not necessarily measurable)
	$l^{\infty}(T)$-valued maps.
\end{itemize}
Then, the following statements hold:
\begin{enumerate}
\item
	\begin{equation*}
		\begin{array}{c}
			\left\{\,
			X_{n} : \Omega_{n}\overset{{\color{white}-}}{\longrightarrow}l^{\infty}(T)\,\right\}_{n\in\N}
		\\
			\overset{{\color{white}.}}{\textnormal{converges weakly to a}}
		\\
			\overset{{\color{white}.}}{\textnormal{tight limit in}}\; \mathcal{M}_{1}\!\left(l^{\infty}(T),\mathcal{B}\right)
		\end{array}
	\quad\Longleftrightarrow\quad
		\begin{array}{l}
			\left\{\,
			X_{n} : \Omega_{n}\overset{{\color{white}-}}{\longrightarrow}l^{\infty}(T)\,\right\}_{n\in\N}
			\;\textnormal{is asymptotically tight, and}
		\\
			\overset{{\color{white}.}}{\textnormal{every finite-dimensional projection of it converges}}
		\\
			\overset{{\color{white}.}}{\textnormal{weakly to a limit Borel probability measure on the}}
		\\
			\overset{{\color{white}.}}{\textnormal{corresponding Euclidean space}}
		\end{array}
	\end{equation*}
\item
	Suppose
	$X : (\Omega,\mathcal{A},\mu) \longrightarrow l^{\infty}(T)$
	is an $l^{\infty}(T)$-valued random variable.
	If
	\,$\left\{\,X_{n} : \Omega_{n}\overset{{\color{white}-}}{\longrightarrow}l^{\infty}(T)\,\right\}_{n\in\N}$
	is asymptotically tight and each of its finite-dimensional projections converges weakly to
	the corresponding finite-dimensional projection of $X$,
	then $X_{n}$ converges weakly to a version of $X$.
\end{enumerate}
\end{theorem}
\proof
\qed

          %%%%% ~~~~~~~~~~~~~~~~~~~~ %%%%%

%\renewcommand{\theenumi}{\alph{enumi}}
%\renewcommand{\labelenumi}{\textnormal{(\theenumi)}$\;\;$}
\renewcommand{\theenumi}{\roman{enumi}}
\renewcommand{\labelenumi}{\textnormal{(\theenumi)}$\;\;$}

          %%%%% ~~~~~~~~~~~~~~~~~~~~ %%%%%
